### 2024-01-10 ms.qmd
Updates
Updates models and functions

@@

# References

>>>>

```{r, cleaning}
#| label: cleaning
source(here("R", "1_data_process.R"))
# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
```

```{r, models}
#| label: models
# fitting the model and extraction of posteriors for both types of task and species using fit_m function
source(here("R", "func.R"))
# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + Associative_Trial*group + (1 + Associative_Trial|lizard_id)
## A.1) L. delicata
deli_asso <- fit_m("asso", "deli")
write.csv(deli_asso, file= "./output/Checking/deli_asso.csv")
## A.2) L. guichenoti
guich_asso <- fit_m("asso", "guich")
write.csv(guich_asso, file= "./output/Checking/guich_asso.csv")
# B) Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + trial_reversal*group + (1 + trial_reversal|lizard_id)
## B.1) L. delicata
deli_rev <- fit_m("rev", "deli")
write.csv(deli_rev, file= "./output/Checking/deli_rev.csv")
## B.2) L. guichenoti
guich_rev <- fit_m("rev", "guich")
write.csv(guich_rev, file= "./output/Checking/guich_rev.csv")
```

```{r, results}
```

```{r, plots}
```

@@

## References
